MRP Case Study

### 2020-03-10 Code/mrp/Case Study .Rmd
Updating stan code.

mrp_sim <- simulate_mrp_data(n=1200)
sample <- mrp_sim[["sample"]]

@@

@@

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code/mrp/generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

@@

>>>>

mrp_sim <- simulate_mrp_data(n=1200)

sample <- mrp_sim[["sample"]]
poststrat <- mrp_sim[["poststrat"]]
true_popn <- mrp_sim[["true_popn"]]

@@

```
```{r}
stan_data <- list( 
  N = nrow(sample), 
  service_failure = sample$service_failure,
  male = sample$male, 
  age = sample$age,
  eth = sample$eth, 
  income = sample$income, 
  state = sample$state)
```

```{r}
fit <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_data,
  seed = 42
)

```
```{r}
fit %>%
  mcmc_trace(
    pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'),
    n_warmup = 500,
    facet_args = list(nrow = 2, labeller = label_parsed)
  )

print(fit, pars = c('alpha','beta1', 'beta2', 'beta3', 'beta4'))
```
```{r}

@@

  gamma_mean = 0.5,                              # Mean for the hyperprior on gamma.
  gamma_var = 0.2,                               # Variance for the hyperprior on gamma.
  tau_min = 0,                                   # Minimum for the hyperprior on tau.
  tau_max = .1,                                   # Maximum for the hyperprior on tau.
  sigma_min = 0,                                 # Minimum for the hyperprior on tau.
  sigma_max = .1                                  # Maximum for the hyperprior on tau.
)
# Generate data.
sim_data <- stan(
  file = here::here("Code", "mrp", "generate_data.stan"),
  data = sim_values,
  iter = 10,
  chains = 1,
  seed = 42,
  algorithm = "Fixed_param"
)

@@

Trying to make the simple model work with the data from the vignette. It seems to not be working but the error code is not clear on why it's not working.

```{r}
stan_values <- list(
  N = 1200,                                       # Number of observations.
  K = 2,                                         # Number of groups.
  I = 65,                                         # Number of observation-level covariates.

  male = sample$male,                 
  eth = sample$eth,      
  age = sample$age,        
  income = sample$income,
  state = sample$state,
  service_failure = sample$service_failure
)

```{r}
fit3 <- stan(
  file = here::here("Code", "mrp", "logit_simple.stan"),
  data = stan_values,
  seed = 42
)
```
